The Inconsistency in \\ G{\"o}del's Ontological Argument \\ --- A Success Story for AI in Metaphysics ---

### 2016-06-22 Papers/2016/IJCAI-Poster/poster.tex
Fix textwidths
Add more rows and fix dimensions
Add screenshots of slides
Adjust horizontal spacing
Adjust vertical spacing
Add summary of results

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
  \begin{document}
  \begin{frame}{}
  \vskip-3ex
    \begin{columns}[t]
      \begin{column}{.49\linewidth}
        \begin{block}{\large Motivation} 
          \includegraphics[width=\textwidth]{VisionLeibniz}
        \end{block}
      \end{column}
      \hfill
      \begin{column}{.48\linewidth}
        \begin{block}{\large Application: Gödel's Ontological Argument
          for the Existence of God}
           \includegraphics[width=\textwidth]{GoedelInconsistency}
        \end{block}
      \end{column}
    \end{columns} \vskip-3ex
    \begin{columns}[t]
      \begin{column}{.33\linewidth}
        \begin{block}{\large Scott's vs. Gödel's Version} 
          \includegraphics[width=\textwidth]{VisionLeibniz}
        \end{block}
      \end{column}
      \hfill
      \begin{column}{.33\linewidth}
        \begin{block}{\large Technique: Semantic Embedding in HOL}
          \includegraphics[width=\textwidth]{SemanticEmbedding}
        \end{block}
      \end{column}
     \begin{column}{.33\linewidth}
        \begin{block}{\large Application: Gödel's Ontological Argument
          for the Existence of God}
           \includegraphics[width=\textwidth]{GoedelInconsistency}
        \end{block}
      \end{column}

>>>>

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
  \begin{document}
  \begin{frame}{}
  \vskip-3ex
    \begin{columns}[t]
      \begin{column}{.5\linewidth}
        \begin{block}{\large Motivation} 
          \includegraphics[width=0.98\textwidth]{./Images/VisionLeibniz}
        \end{block}
      \end{column}
      \hfill
      \begin{column}{.48\linewidth}
        \begin{block}{\large Application: Gödel's Ontological
            Argument} \centering
           \includegraphics[width=0.98\textwidth]{./Images/GoedelInconsistency}
        \end{block}
      \end{column}
    \end{columns} 
    \begin{columns}[t]
      \begin{column}{.33\linewidth}
        \begin{block}{\large Scott's and Gödel's Versions} 
          \includegraphics[width=0.98\textwidth]{./Images/Scott_vs_Goedel}
        \end{block}
      \end{column}
      %\hfill
      \begin{column}{.33\linewidth}
        \begin{block}{\large Approach: Semantic Embedding}
          \includegraphics[width=0.98\textwidth]{./Images/SemanticEmbedding}
        \end{block}
      \end{column}
     \begin{column}{.33\linewidth}
        \begin{block}{\large Standard Translation of Modal Logic}
           \includegraphics[width=0.98\textwidth]{./Images/StandardTranslation}
        \end{block}
      \end{column}
    \end{columns}
    \begin{columns}[t]
      \begin{column}{.33\linewidth}
        \begin{block}{\large Modal Logic in Isabelle} 
          \includegraphics[width=0.98\textwidth]{./Images/ModalLogicInIsabelle}
        \end{block}
      \end{column}
      %\hfill
      \begin{column}{.33\linewidth}
        \begin{block}{\large Scott's Version in Isabelle}
          \vspace{25pt}
          \includegraphics[width=0.98\textwidth]{./Images/ScottInIsabelle}
          \vspace{35pt}
        \end{block}
      \end{column}
     \begin{column}{.33\linewidth}
        \begin{block}{\large LEO-II's Refutation of Gödel's Axioms}
           \includegraphics[width=0.98\textwidth]{./Images/Refutation}
        \end{block}
      \end{column}
    \end{columns}
    \begin{columns}[t]
      \begin{column}{.33\linewidth}
        \begin{block}{\large Refutation Reconstruction in Isabelle} 
          \includegraphics[width=0.98\textwidth]{./Images/IsabelleRefutation}
        \end{block}
      \end{column}
      %\hfill
      \begin{column}{.33\linewidth}
        \begin{block}{\large Explaining the Inconsistency}
          \includegraphics[width=0.98\textwidth]{./Images/Explanation}
          \vspace{75pt}
        \end{block}
      \end{column}
     \begin{column}{.33\linewidth}
        \begin{block}{\large Summary of Results}
           \begin{itemize}
              \item Inconsistency of G\"odel's original axioms has now been verified
              \item Reason for inconsistency is finally well understood and explained
              \item Reconstruction of the refutation in Isabelle led to various user interface and performence improvements for the embedding of modal logic in Isabelle
              \item Higher-order interactive and automated reasoning technology is ready for applications in philosophy
           \end{itemize}
           \vspace{25pt}
        \end{block}
      \end{column}
    \end{columns}
